---
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
info <- fromJSON("info.json")
firstname <- info$firstName
middlename <- info$middleName
lastname <- info$lastName
nickname <- info$nickname
phone <- info$phone
```
---
title: "`r firstname` `r middlename` `r lastname`"
output: pdf_document
fontfamily: arev
geometry: margin=1cm
header-includes:
 - \usepackage{fontawesome}
---
\pagenumbering{gobble}
\begin{center}
\faEnvelope{\space} \href{mailto:`r nickname`@gmail.com}{`r nickname`@gmail.com} |
\faPhone{\space} `r phone` | 
\faGithub{\space} \href{https://github.com/`r nickname`}{`r nickname`} | 
\faLinkedin{\space} \href{https://www.linkedin.com/in/`r firstname`-`r middlename`-`r lastname`}{www.linkedin.com/in/`r firstname`-`r middlename`-`r lastname`}
\end{center}

## Education

**Certificate Program in Database and Data Analytics**

UC Santa Cruz Silicon Valley Extension, Santa Clara, CA, 2017 – 2018

* Courses:
    + Hadoop: Distributed Processing of Big Data
    + Apache Spark with Scala
    + Data Analysis, Introduction (R)
    + Introduction to Machine Learning and Data Mining
    + Predictive Analytics: Applications of Machine Learning

**Bachelor of Science in Electrical Engineering**

Monterrey Institute of Technology and Higher Education, Guadalajara, Mexico, 1999–2003

  * Graduated with Honors.

## Skills

```{r skill_table, echo=FALSE}
#library(knitr)
#library(kableExtra)
skills <- read.csv("skills_base.csv",as.is=TRUE,check.names=FALSE)
knitr::kable(skills)
# Find out why when I include this the custom latex doesn't work:
#kableExtra::row_spec(knitr::kable(skills,format="markdown"),0,bold=TRUE)
```

## Professional Experience

**Principal Software Engineer, Cadence (Sept 2015 – Current)**

Current project is a PCIe Protocol Model written in C. Code has a lot of legacy from many years and it is around 400,000 lines. It targets Linux systems.

  * Architected and developed many features of the code.
  * Tracked, debugged and fixed several customer issues using the JIRA system.
  * Trained junior engineers and conducted code reviews as needed.
  * Developed a Code Analytics engine that scrapes the repository (17 years of history) and identifies hotspots of the code based on the number of edits. A decision tree model is built. Written in Python and R.

**Component Design Engineer, Intel Corporation (Feb 2009 – Sept 2015)**

Worked on design and verification of a PCIe/USB/SATA PHY, a Server Processor and a GPU.

Coded a pre-silicon test environment in a mixture of C/C++, System Verilog and Perl scripts.

  * Developed a library of base classes which were the foundation for a random test environment.
  * Coded wrappers to interface C++ code to a digital logic simulator.
  * Coded Perl scripts to automate the simulation/checking process.
  
## Projects

**Wind Analysis Of Northern Yucatan Coast for Kiteboarding (Dec 2018)**

Spark SQL project written in a Jupyter notebook. It uses a very innovative method to convert an irregular time series into an equally spaced time series for easy computation of time intervals. Covers 10 years of data.

https://github.com/`r nickname`/windMining/blob/master/kbWindNorYuc/kbWindNorYuc.ipynb
