---
output:
  pdf_document: default
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
info <- fromJSON("info.json")
firstname <- info$firstName
middlename <- info$middleName
lastname <- info$lastName
nickname <- info$nickname
phone <- info$phone
```
---
title: "`r firstname` `r middlename` `r lastname`"
output: pdf_document
fontfamily: arev
geometry: margin=1cm
header-includes:
 - \usepackage{fontawesome}
---
\pagenumbering{gobble}
\begin{center}
\faEnvelope{\space} \href{mailto:`r nickname`@gmail.com}{`r nickname`@gmail.com} |
\faPhone{\space} `r phone` | 
\faGithub{\space} \href{https://github.com/`r nickname`}{`r nickname`} | 
\faLinkedin{\space} \href{https://www.linkedin.com/in/`r firstname`-`r middlename`-`r lastname`}{www.linkedin.com/in/`r firstname`-`r middlename`-`r lastname`}
\end{center}

## Education

```{r child = 'education_long.Rmd'}
```

## Skills

```{r skill_table, echo=FALSE}
#library(knitr)
#library(kableExtra)
skills <- read.csv("skills_three.csv",as.is=TRUE,check.names=FALSE)
knitr::kable(skills)
# Find out why when I include this the custom latex doesn't work:
#kableExtra::row_spec(knitr::kable(skills,format="markdown"),0,bold=TRUE)
```

## Professional Experience

```{r child = 'professional_exp_shuffle.Rmd'}
```
  
## Projects

**Wind Analysis Of Northern Yucatan Coast for Kiteboarding (Dec 2018)**

Spark SQL project written in a Jupyter notebook. It uses a very innovative method to convert an irregular time series into an equally spaced time series for easy computation of time intervals. Covers 10 years of data.

https://github.com/`r nickname`/windMining/blob/master/kbWindNorYuc/kbWindNorYuc.ipynb
